### 2020-05-10 ncov.tex
done?

We ran 4 independent Markov Chain Monte Carlo chains each consisting of 500,000 burnin steps and 500,000 sampling steps.
Posterior samples are thinned every 1000 steps to remove autocorrelations among posterior samples.
Convergence is assessed by ensuring that the Gelman-Rubin statistic is below 1.01  \citep{gelman1992inference} and the effective sample size is greater than 1000 for all hyperparameters ($\mu_r, \mu_G, \mu_\kappa, \sigma_r, \sigma_G, \sigma_\kappa$);
trace plots and marginal posterior distribution plots are presented in Appendix.
95\% credible intervals (CI) are calculated by computing 2.5\% and 97.5\% quantiles from the marginal posterior distribution for each hyperparameter.

>>>>

We ran 4 independent Markov Chain Monte Carlo chains each consisting of 500,000 burnin steps and 500,000 sampling steps using Metropolis-Hastings algorithm.
Proposal distributions are modeled using independent normal distributions.
Initial values and variances of the proposal distributions are chosen by trial-and-error to ensure reasonable acceptance rate (around 10\%) and convergence within 1,000,000 steps.
Posterior samples are thinned every 1000 steps to remove autocorrelations among posterior samples.
Convergence is assessed by ensuring that the Gelman-Rubin statistic is below 1.01  \citep{gelman1992inference} and the effective sample size is greater than 1000 for all hyperparameters ($\mu_r, \mu_G, \mu_\kappa, \sigma_r, \sigma_G, \sigma_\kappa$);
trace plots and marginal posterior distribution plots are presented in Appendix.
95\% credible intervals (CI) are calculated by computing 2.5\% and 97.5\% quantiles from the marginal posterior distribution for each hyperparameter.
